Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-05-16 paperDistance/paper.tex
assumption discussion needs work

In Section~\ref{sec:method} we listed a set of assumptions upon which
the photometric parallax method in this project is based.
Here we return to these assumptions, and discuss them critically in more
detail.
\begin{description}
\item[stationarity] Stationarity assumes both the low and high
  signal to noise objects are being drawn from the same distribution,
  independent of noise. This isn't precisely true because most
  \gaia\ objects have similar noise $(\sim 3 \, \mathrm{mas})$, but
  their signal (parallax) depends on their distance. Nearby stars have
  higher signal (parallax) because they are closer and the nearby
  stars are mostly main sequence stars due to the IMF, timing, and
  malmquist bias. However, we can see bright giants to much larger
  distances, and therefore lower signal or parallax, leading to lower
  signal to noise. So the red giant branch is a population of
  relatively lower signal to noise objects compared with the main
  sequence. But this does not violate the stationarity assumption in
  detail, because the low and high signal to noise objects have to be
  drawn from the same distribution within some feature or patch of the
  space. This is all assuming the Gaia noise model is correct. If the
  uncertainties are over estimated then we could be over deconvolving
  (generating a tighter distribution than the truth) And in some
  extreme over estimate of uncertainties the lower signal to noise
  giants could be pulled to the main sequence. But with the quoted
  uncertainties this seems unlikely. As you move up the giant branch,
  and probe farther giants, the signal to noise will continue to
  diminish, but because the color uncertainties are not large, the S/N
  spread within a patch of the \cmd\ is well mixed. Possibly a
  metallicity trend with distance, placing more nearby (higher S/N)
  objects at slightly different positions on the CMD pulling lower S/N
  objects to that distribution for our prior. But if something has
  small error bars is good data is good data both for inference and
  generating the prior

>>>>

\subsection{Critical discussion of assumptions}

In Section~\ref{sec:method} we listed a set of assumptions upon which
the photometric parallax method in this project is based.
Here we return to these assumptions, and discuss them critically in more
detail.
\begin{description}
\item[stationarity] (HOGG needs to clean this paragraph)
  We have assumed that (locally) the morphology of
  the \cmd\ is independent of signal-to-noise; that is, we have assumed that
  both the low and high
  signal-to-noise objects are being drawn from the same distribution.
  This isn't precisely true because nearby stars in \tgas\ are
  mostly main sequence stars, while we can see luminous giants to much larger
  distances. So the red giant branch is a population of
  relatively lower signal to noise objects compared with the main
  sequence. This does not violate the stationarity assumption in
  detail, because the low and high signal to noise objects have to be
  drawn from the same distribution within some feature or patch of the
  space. This is all assuming the Gaia noise model is correct. If the
  uncertainties are over estimated then we could be over deconvolving
  (generating a tighter distribution than the truth) And in some
  extreme over estimate of uncertainties the lower signal to noise
  giants could be pulled to the main sequence. But with the quoted
  uncertainties this seems unlikely. As you move up the giant branch,
  and probe farther giants, the signal to noise will continue to
  diminish, but because the color uncertainties are not large, the S/N
  spread within a patch of the \cmd\ is well mixed. Possibly a
  metallicity trend with distance, placing more nearby (higher S/N)
  objects at slightly different positions on the CMD pulling lower S/N
  objects to that distribution for our prior. But if something has
  small error bars it is good data is good data both for inference and
  generating the prior.
